### 2012-07-31 Doc/VRIPHYS2012/vriphys2012.tex
rewritten contributon, new images for the paper
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@440 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

Methods based on continuum mechanics and namely theory of elasticity gained on popularity in real-time simulations ever since Terzopoulos \cite{Terzopoulos1987} presented his work on elastic deformation modeling.
While the methods using finite elements and theory of elasticity are fairly popular in volumetric modeling of deformations \cite{Cotin1999,Nesme2006,Miller2007}, they are still frowned upon in the area of thin structures. 
Yet, a special field of continuum mechanics has studied the deformations of these objects, and has proposed models based on shell theory.
This theory was integrated numerically \CD{Todo citation of a shell book} using Finite Elements, but there are two issues for obtaining interactive frame rates: 
(i) the continuum equations requires second spatial derivations that can not be handled with linear interpolation and 
(ii) the final system of equations that describes the mechanics is non-linear (if the deformations are not small).

@@

% TODO
The main contributions of the paper are following \CD{- Tomas, you need to write sentences here -}

\begin{itemize}
    % not really novel, similar model already in Ubach2010
    %\item shell element based on Bézier triangles
    \item Our element solves the problems of the element presented by Comas
        \cite{Comas2010c}: it is continuous on the element boundary and has
        all rotational degrees of freedom.

    % TODO: needs better explanation
    \item Two stage interpolation: 6DOF nodes -> bezier points -> bezier
        triangle

    % + separation between nodes and dofs
    %\item The model separates nodes of the mesh from degrees of freedom of the
    %    control mesh. This allows mapping a surface on deformable skeleton.

    % + mapping: smooth surface results with less shells + collision response
    %   on smooth surface 
    \item Mapping of high resolution mesh on the curved surface of the
        shell. The smooth mapped surface can be used for collision
        detection and allows the propagation of proper collision response
        back onto the (low resolution) mechanical mesh.

@@

In this subsection we propose an element featuring interpolation with high degree of flexibility while still maintaining low number of degrees of freedom.
We introduce a new way of building the interpolation by using two stages 
\CD{ - Need a figure here - }:
\begin{enumerate}
    \item A B\'ezier interpolation with cubic polynomial functions is defined on a triangle.
    \item A kinematic relation between nodes (6DOFs) defined at the vertices and the control points of the B\'ezier triangle.
\end{enumerate}

@@

\Figure{0.8\linewidth}{bezier}
{Cubic B\'ezier triangle with mesh of 10 control points.}

@@

\Figure{0.8\linewidth}{segments}
{Correspondence between edge points and associated corner points shown in
blue. \CD{Not clear !!}}

@@

\Figure{\linewidth}{roof}
{Convergence for modified Scordelis-Lo roof test of DKT+ANDES element and
our B\'ezier shell element. \CD{Can you do the same test with the model used by Comas ?}}

@@

\Figure{\linewidth}{hemisphere}
{Convergence for test on hemisphere with 18° hole for the DKT+ANDES element and
our B\'ezier shell element. \CD{Same question: can you do the same test with the model we used with O.Comas ? Hopefully, it will show that our model has a better convergence ... }}

>>>>

Methods based on continuum mechanics and namely theory of elasticity gained on popularity in real-time simulations ever since Terzopoulos \cite{Terzopoulos1987} presented his work on elastic deformation modeling.
While the methods using finite elements and theory of elasticity are fairly popular in volumetric modeling of deformations \cite{Cotin1999,Nesme2006,Miller2007}, they are still frowned upon in the area of thin structures. 
Yet, a special field of continuum mechanics has studied the deformations of these objects, and has proposed models based on shell theory.
This theory was integrated numerically using Finite Elements \cite{Reddy1993}, but there are two issues for obtaining interactive frame rates: 
(i) the continuum equations requires second spatial derivations that can not be handled with linear interpolation and 
(ii) the final system of equations that describes the mechanics is non-linear (if the deformations are not small).

@@

Extending the work of Comas \cite{Comas2010c} we have designed a shell element that uses B\'ezier interpolation polynomials.
Our element solves the problems of the element presented by Comas:
(i) it uses all 6 degrees of freedom,
(ii) the deformations are completly symmetric and
(iii) the boundary between elements is continuous.
We present a two stage interpolation:
(i) first a kinematic link between 6 DOF nodes of element and nodes of B \'ezier control mesh is defined and
(ii) interpolation function of cubic B\'ezier triangle is applied to interpolate on the surface of the element.
Mapping of high resolution mesh on the curved surface of the shell.
Finally from the kinematic link we derive formulas for
(i) interpolating velocity on the element surface and for
(ii) distribution of normal force applied on the element surface back to 6 DOF nodes of the element.
This allows us to use smooth mapped surface for collision detection and allows the propagation of proper collision response back onto the mechanical mesh.

@@

In this subsection we propose an element featuring interpolation with high degree of flexibility while still maintaining low number of degrees of freedom.
We introduce a new way of building the interpolation by using two stages

\begin{enumerate}
    \item A B\'ezier interpolation with cubic polynomial functions is defined on a triangle.
    \item A kinematic relation between nodes (6DOFs) defined at the vertices and the control points of the B\'ezier triangle.
\end{enumerate}

\FigureWI{stages}
{Two stages of interpolation: First, from triangular with 6DOF nodes (a) a mesh of control points (b) is computed.
Then based on definition of the B\'ezier triangle a surface is interpolated.}

@@

%\Figure{0.8\linewidth}{bezier}
%{Cubic B\'ezier triangle with mesh of 10 control points.}

\Figure{0.8\linewidth}{bezier2}
{Cubic B\'ezier triangle with mesh of 10 control points.}

@@

%\Figure{0.8\linewidth}{segments}
%{Correspondence between edge points and associated corner points shown in
%blue. \CD{Not clear !!}}

\Figure{0.8\linewidth}{segments2}
{Internal nodes of control mesh are connected to the corner nodes by kinematic link (shown in blue).}

@@

\Figure{\linewidth}{roof}
{Convergence for modified Scordelis-Lo roof test of DKT+ANDES element, 
our B\'ezier shell element (BSH) and elemnt of O. Comas (PSH) with polynomial shape function.}

\Figure{\linewidth}{roof-img}
{Coloured plot of vertical displacement in the roof test}

@@

\Figure{\linewidth}{hemisphere}
{Convergence for test on hemisphere with 18° hole for the DKT+ANDES element and
our B\'ezier shell element (BSH) and elemnt of O. Comas (PSH) with polynomial shape function.}

\Figure{\linewidth}{hemisphere-img}
{Coloured plot of radial displacement in the hemisphere test}
